
% Place the contents of your abstract between the
% \begin{abstract} and \end{abstract} decorators.

\begin{abstract}

% The abstract should be between four and seven sentences long. Introduce the
% problem you are studying. Describe what you did. Summarize your results --- what
% did you discover, what is the main take-away message? Basically, you're trying 
% to sell your paper to the reader, so be brief and to the point. \textbf{Do \emph{not}
% include any citations in the abstract.}

% % The \textbf{} command makes the specified text bold. The \emph{} or
% % \textit{} command are used to italicize text. In general, text is never
% % underlined.

% % DON'T FORGET TO MATCH EACH OPEN BRACE WITH A CLOSING BRACE!

Video games are often seen as an ethereal space, a medium where anyone can be or do anything, without conforming to the science, physics, or social structures of the real world. However, just as Machine Learning models are not completely “objective” or free from bias, video games are created by developers who may embed inequalities in game narratives, character design, and the in-game statistics and mechanics. In particular, a character’s gender may be highly correlated with certain stats or roles. Our project aims to test this hypothesis as a Machine learning classification problem. Here the target variable is the label character of the gender and the features include quantitative stats (health, defense, strength, etc), and other factors such as their role and difficulty, etc. In order to achieve this task, we used Machine Learning to train classification models using several techniques, including Random Forest Decision Trees, K-Nearest Neighbors, and Support Vector Machines. Our best model, a SVM with RBF kernel, had an accuracy of 63\% and a weighted F1 score of 0.64. While our results were moderately accurate at predicting video game character genders, they were less accurate in predicting underrepresented female characters compared to male characters. Still, this paper takes a novel approach towards gender analysis in video games, and highlights the possibilities of embedded biases in video game development and character design. 

\end{abstract}

