% In this section, you should introduce the reader to the problem you
% are attempting to solve. For example, for the first project: describe
% the dataset, and the prediction problem that you are
% investigating. You should also cite and briefly describe other related
% papers that have tackled this problem (or similar ones) in the past
% --- things that came up during the course of your research. In the
% AAAI style, citations look like \cite{aima} (see
% the comments in the source file \texttt{intro.tex} to see how this
% citation was produced). Conclude by summarizing how the
% remainder of the paper is organized. \\

% % Citations: As you can see above, you create a citation by using the
% % \cite{} command. Inside the braces, you provide a "key" that is
% % uniue to the paper/book/resource you are citing. How do you
% % associate a key with a specific paper? You do so in a separate bib
% % file --- for this document, the bib file is called
% % project1.bib. Open that file to continue reading...

% % Note that merely hitting the "return" key will not start a new line
% % in LaTeX. To break a line, you need to end it with \\. To begin a 
% % new paragraph, end a line with \\, leave a blank
% % line, and then start the next line (like in this example).
% Overall, the aim in this section is context-setting: what is the
% big-picture surrounding the problem you are tackling here?

% The \section{} command formats and sets the title of this
% section. We'll deal with labels later.
\section{Introduction}
\label{sec:intro}

Video games have been a topic of interest to scholars from several disciplines, such as in media studies, Psychology, Sociology, Computer Graphics and Computer Science, and more. Media and film scholars have analyzed how narratives can be told through gameplay and other mediums, and Sociologists examine communities and social elements from online gaming. While video games allow players to assume new identities, the gaming sphere is a stereotypically masculine space that often mirrors social structures of the real world. Video game developers may design and create characters with different stats, abilities, and roles depending on the character demographics, such as gender. In this paper, we utilize a Machine Learning approach to classifying character genders from 5 Multiplayer Online Battleground Arena (MOBA) video games. We built a dataset using character stats and attributes, such as their Health Points, attack types, and more, as detailed in our Data Exploration section. We then use this data to train several classification models, such as Random Forest, K-Nearest Neighbors, and Support Vector Machines, to predict gender. Our goal is to see whether our classification models can distinguish character genders, highlighting how video game characters may have noticeable and predictable differences based on their gender.